\section{Results of Prior SBIR/STTR Supported Research}
\label{sec:prior}

All information in this section
about other companies (Hearing Emulations, LLC, and
Exegy, Inc.), including quantities of both external and internal investments,
is proprietary to those firms.

\medskip

\noindent
{\bf Hearing Aids Based on Models of Cochlear Compression} --
SBIR Phase I (1999), \$100,000, and Phase II (2001), \$546,284.
PI: Julius Goldstein, Senior Personnel: Roger D. Chamberlain.

This research demonstrated improvements in the understandability of speech in
noisy environments for hearing-impaired individuals.
Commercialization of this work resulted in the formulation of a new
company, Hearing Emulations, LLC, which subsequently received private
investment of approximately \$2 million.
BECS's interest was sold to the investors, so we no longer
have visibility into the company.
Publications resulting from this work
include~\cite{cgi03,gogv03,gvc01,gvcgi00}.
Patents resulting from this work
include~\cite{Goldstein05a,Goldstein05b,gc03}.

\medskip

\noindent
{\bf Fast Biosequence Annotation via Reconfigurable Hardware} --
STTR Phase I (2004), \$307,508, and Phase II (2007), \$510,614.
PI: Jeremy Buhler, Senior Personnel: Roger D. Chamberlain.

This research resulted in FPGA-based accelerated implementations of
several biosequence applications, including both DNA and protein alignment
as well as RNA folding.
Commercialization of this work resulted in a Memorandum of Understanding (MOU)
between Exegy, Inc., and BECS.  Exegy has subsequently invested
approximately \$500,000 in the technology.
Under the terms of the MOU, Exegy
is not required to disclose sales figures to BECS.
Publications resulting from this work
include~\cite{bljc07,dlmbc10,hjlbc07,jbc08,jlbc07b,jlbc07a,jlbhc08,jbc09,jbc10b,jbc10a,kbcfgl04,kbcfgjl07,lbc05,lbc09},
which includes a best paper award~\cite{jbc10b}.
Patents resulting from this work
include~\cite{Buhler11,Buhler13,Buhler17} and one pending application.
